Synthesis of Rules for Network Intrusion Detectors

### 2019-10-24 paper/paper.tex
pass on multiple parts

\begin{document}
%
\title{Synthesis of Rules for Network Intrusion Detectors}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Alcantara\Comment{\inst{1}}\Comment{\orcidID{0000-1111-2222-3333}} \and
Guilherme Padilha\Comment{\inst{1}}\Comment{\orcidID{1111-2222-3333-4444}} \and
Marcelo d'Amorim\Comment{\orcidID{0000-0002-1323-8769}}}
%
\authorrunning{Alcantara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Federal University of Pernambuco (UFPE), Recife, Brazil\\
\email{\{lama,ghps,damorim\}@cin.ufpe.br}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the network
traffic against a pre-defined set of rules, which can become obsolete
as attackers learn new strategies to circumvent existing defenses.
This paper proposes \tname{}, a technique that automatically
synthesizes \nids\ rules from positive and negative examples (\ie{},
malicious and benign traffic). \tname{} formulates synthesis as an
optimization problem whose candidate solutions are rules that
maximizes the captured the positive traffic and minimizes the captured
negative traffic. \tname{} bootstraps the search with candidate
solutions that use data from the payload of the malicious message and
produces optimal rule candidates on output. We evaluated \tname{} on a
diverse set of attacks. Results indicate that \Fix{...}

@@

In the following, we illustrate how \tname{} proceeds for obtaining
the rule for the SYN Flood attack. The main challenge in synthesizing
rules is to discover the set of options that enables the \nids\ to
capture the malicious traffic, but ignore the benign traffic.  The
other parts of the rule (\ie{}, the action and the header) are either
inferred or left constant. \tname{} sets the action header to
\CodeIn{alert} and sets the header to \CodeIn{<proto> any any -> any
  any}, indicating that it infers the target protocol, and it uses the
most general flow description possible, \ie{}, analyzing the traffic
flowing from/to any address and port.  We conjecture that the system
administrator would know how to modify the constant parts.

\tname{} starts the search for rule options for the SYN Flood attack
from the initial set of options appearing below.

@@

This set is based on an analysis of the packets from the positive
traffic. Consequently, a rule that uses this set of options would
capture the positive traffic by construction. Unfortunately, such rule
would be overspecified. It would unlikely capture different
manifestations of the same attack. Informally, the rule includes ``too
many'' characteristics of the malicious traffic used to define it, but
new attacks may not use the same data. To address that, \tname{}
minimizes the rule with the goal of finding the minimal set of rules
that only captures the positive traffic, hence mitigating the
overfitting problem. \tname{} potentially finds several minimal
rules. The list below shows the options for the five shortest rules it
produces for this attack.

>>>>

\begin{document}
%
\title{Synthesis of Rules for Network Intrusion Detectors}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Alcantara\Comment{\inst{1}}\Comment{\orcidID{0000-1111-2222-3333}} \and
Guilherme Padilha\Comment{\inst{1}}\Comment{\orcidID{1111-2222-3333-4444}} \and
Marcelo d'Amorim\Comment{\orcidID{0000-0002-1323-8769}}}
%
\authorrunning{Alcantara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Federal University of Pernambuco (UFPE), Recife, Brazil\\
\email{\{lama,ghps,damorim\}@cin.ufpe.br}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the network
traffic against a pre-defined set of rules, which can become obsolete
as attackers learn new strategies to circumvent existing defenses.
This paper proposes \tname{}\footnote{Abbreviation of \textbf{Sy}nthesis of
  Su\textbf{ri}cata R\textbf{u}le\textbf{s}.}, a technique that automatically
synthesizes \nids\ rules from positive and negative examples (\ie{},
malicious and benign traffic). \tname{} formulates synthesis as an
optimization problem whose candidate solutions are rules that
maximizes the captured the positive traffic and minimizes the captured
negative traffic. \tname{} bootstraps the search with candidate
solutions that use data from the payload of the malicious message and
produces optimal rule candidates on output. We evaluated \tname{} on a
diverse set of attacks. Results indicate that \Fix{...}

@@

In the following, we illustrate how \tname{} proceeds for obtaining
the rule for the SYN Flood attack. The main challenge in synthesizing
rules is to discover the set of options that enables the \nids\ to
capture the malicious traffic, but ignore the benign traffic.  The
other parts of the rule (\ie{}, the action and the header) are either
inferred or left constant. \tname{} sets the action header to
\CodeIn{alert} and sets the header to \CodeIn{<proto> any any -> any
  any}, indicating that it infers the target protocol and uses the
most general flow description possible, \ie{}, it instructs the
\nids\ to analyze the traffic flowing from/to any address and port.
We understand that this is domain-specific information and conjecture
that the system administrator would know how to modify the constant
parts.

\tname{} proceeds as follows to synthesize rules for the SYN Flood
attack. First, it analyzes the positive traffic and extracts options
expressed in that traffic. For this example, it finds the following
set of options:

@@

Note that a rule that uses this set of options would capture the
positive traffic as these options originated from the positive
traffic. Unfortunately, such rule would be overspecified. It would
unlikely capture different manifestations of the same
attack. Informally, the rule includes ``too many'' characteristics of
the malicious traffic used to define it. To address this overfitting
issue, \tname{} minimizes the rule preserving the invariant that
plausible rules should only capture the positive traffic. \tname{}
potentially finds several minimal rules. The list below shows the
options for the five shortest rules it produces for this attack.
